---
title: "R Notebook"
output: html_notebook
---

```{r}
library(ISLR)
library(lsr)
```

```{r}
dataCredit <- Credit
head(dataCredit)
```

#1 Mean and Median of Rating, Cards, and Age
```{r}
mean(dataCredit$Rating)
```
```{r}
mean(dataCredit$Cards)
```
```{r}
mean(dataCredit$Age)
```
```{r}
median(dataCredit$Rating)
```
```{r}
median(dataCredit$Cards)
```
```{r}
median(dataCredit$Age)
```

#2 Mode of Gender, Student, and Married
```{r}
modeOf(dataCredit$Gender)
```
```{r}
modeOf(dataCredit$Student)
```
```{r}
modeOf(dataCredit$Married)
```

#3 Sample 10,37, and 91 Percentiles of Education
Percentile 10
```{r}
quantile(x = dataCredit$Education, probs = 0.1)
```
Percentile 37
```{r}
quantile(x = dataCredit$Education, probs = 0.37)
```
Percentile 91
```{r}
quantile(x = dataCredit$Education, probs = 0.91)
```
#4 Quartiles of Balance and its corresponding boxplot
Kuartil
```{r}
quantile(x = dataCredit$Balance, probs = c(0.25,0.50,0.75))
```
Boxplot
```{r}
boxplot(x = dataCredit$Balance)
```
#5 Correlation and the scatter plot between pairs of Limit and Rating, Age and Card, Income and Education
Limit and Rating
```{r}
newData1 <- data.frame(Limit = dataCredit$Limit, Rating = dataCredit$Rating)
newData1
```
```{r}
cor(newData1)
```
```{r}
plot(newData1$Limit, newData1$Rating)
```
Age and Card
```{r}
newData2 <- data.frame(Age = dataCredit$Age, Card = dataCredit$Cards)
newData2
```
```{r}
cor(newData2)
```
```{r}
plot(newData2$Age, newData2$Card)
```
Income and Education
```{r}
newData3 <- data.frame(Income = dataCredit$Income, Education = dataCredit$Education)
newData3
```
```{r}
cor(newData3)
```
```{r}
plot(newData3$Income, newData3$Education)
```

#6 Soal Probabilitas
Sebuah dadu dilemparkan sebanyak 10 kali, tentukan probabilitas dari peristiwa muncul mata dadu 4 sebanyak 4 kali
- n = 10, p = 1/6 (Peluang tiap sisi nya adalah sama yaitu 1/6), x = 4

```{r}
dbinom(x = 4, size = 10, prob = 1/6)
```

















































